\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-01-24 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english]{book}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{babel}
\usepackage{float}
\usepackage{textcomp}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},backref=section,colorlinks=false,pdfpagemode=None]
 {hyperref}
\hypersetup{
 pdftex,pdfstartview=FitH,pdfpagelayout=SinglePage}
\usepackage{breakurl}

@@

Since then it has been developed and maintained by a development team:
in alphabetical order, Jean-Paul (Pablo) Ampuero, Piero Basini, Céline
Blitz, Ebru Bozda\u{g}, Emanuele Casarotti, Joseph Charles, Min Chen,
Percy Galvez, Dominik Göddeke, Vala Hjörleifsdóttir, Sue Kientz, Dimitri
Komatitsch, Jesús Labarta, Nicolas Le Goff, Pieyre Le Loher, Qinya
Liu, Yang Luo, Alessia Maggi, Federica Magnoni, Roland Martin, René
Matzen, Dennis McRitchie, Matthias Meschede, Peter Messmer, David
Michéa, Surendra Nadh Somala, Tarje Nissen-Meyer, Daniel Peter, Max
Rietmann, Elliott Sales de Andrade, Brian Savage, Bernhard Schuberth,
Anne Sieminski, Leif Strand, Carl Tape, Jeroen Tromp, Jean-Pierre
Vilotte, Zhinan Xie, Hejun Zhu.\\

@@

@@

solids are supported.

@@

If you use PML, the mesh elements that belong to the PML layers can
be acoustic or elastic, but not viscoelastic nor poroelastic. Then,
when defining your model, you should define these absorbing elements
as either acoustic or elastic. In you forget to do that, the code
will fix the problem by automatically converting the viscoelastic
or poroelastic PML elements to elastic. This means that strictly speaking
the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the
entrance of the PML, but in practice this is sufficient and produces
only tiny / negligible spurious reflections.

>>>>

% !TEX encoding = IsoLatin
%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english]{book}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{babel}
\usepackage{float}
\usepackage{textcomp}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},backref=section,colorlinks=false,pdfpagemode=None]
 {hyperref}
\hypersetup{
 pdftex,pdfstartview=FitH,pdfpagelayout=SinglePage}
\usepackage{breakurl}

@@

Since then it has been developed and maintained by a development team:
in alphabetical order, Jean-Paul (Pablo) Ampuero, Piero Basini, Céline
Blitz, Ebru Bozda\u{g}, Emanuele Casarotti, Joseph Charles, Min Chen,
Percy Galvez, Dominik Göddeke, Vala Hjörleifsdóttir, Sue Kientz, Dimitri
Komatitsch, Jesús Labarta, Nicolas Le Goff, Pieyre Le Loher, Matthieu
Lefebvre, Qinya Liu, Yang Luo, Alessia Maggi, Federica Magnoni, Roland
Martin, René Matzen, Dennis McRitchie, Matthias Meschede, Peter Messmer, 
David Michéa, Surendra Nadh Somala, Tarje Nissen-Meyer, Daniel Peter, Max
Rietmann, Elliott Sales de Andrade, Brian Savage, Bernhard Schuberth,
Anne Sieminski, Leif Strand, Carl Tape, Jeroen Tromp, Jean-Pierre
Vilotte, Zhinan Xie, Hejun Zhu.\\

@@

\section{Using the ADIOS library for I/O}
Regular POSIX I/O can be problematic when dealing with large simulations one large
clusters (typically more than $10,000$ processes). SPECFEM3D use the ADIOS library~\cite{Liu2013}
to deal transparently take advantage of advanced paralllel file system features. To enable
ADIOS, the following steps should be done:
\begin{enumerate}
\item Install ADIOS (available from \url{https://www.olcf.ornl.gov/center-projects/adios/}). 
Make sure that your environment variables reference it. 
\item You may want to change ADIOS related values in the \texttt{constants.h.in} file.
The default values probably suit most cases.
\item Configure using the \texttt{--with-adios} flag.
\end{enumerate}
ADIOS is currently only usable for meshfem3D generated mesh (i.e. not for meshes generated
with CUBTI). Additional control parameters are discussed in section~\ref{cha:Main-Parameter}.

@@

solids are supported. Note that xmeshfem3d generated meshes do not support C-PML yet.

@@

\item [\texttt{ADIOS\_ENABLED}] Turn this flag on to enable ADIOS. If set to \texttt{.false.}, subsequent ADIOS 
parameters will not be considered.
\item [\texttt{ADIOS\_FOR\_DATABASES}] Turn this flag on to use ADIOS for xmeshfem3D output and 
xgenerate\_database input.
\item [\texttt{ADIOS\_FOR\_MESH}]  Turn this flag on to use ADIOS for generated databases.
\item [\texttt{ADIOS\_FOR\_FORWARD\_ARRAYS}] Turn this flag on to read and write forward arrays using ADIOS.
\item [\texttt{ADIOS\_FOR\_KERNELS}] Turn this flag on to produce ADIOS kernels that can later be visualized with the ADIOS version of combine\_vol\_data.

\end{description}
If you use PML, the mesh elements that belong to the PML layers can
be acoustic or elastic, but not viscoelastic nor poroelastic. Then,
when defining your model, you should define these absorbing elements
as either acoustic or elastic. In you forget to do that, the code
will fix the problem by automatically converting the viscoelastic
or poroelastic PML elements to elastic. This means that strictly speaking
the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the
entrance of the PML, but in practice this is sufficient and produces
only tiny / negligible spurious reflections.
